### 2020-11-15 Thesis-Chapter5-ThreatModel.tex
Finish chapter 5

This chapter consists of a threat model and analysis of a specific device key escrow \ac{EA} proposal, Stefan Savage's
``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion'' \cite{savage_lawful_2018}.
Lacking a concise name, this proposal will be referred to by its acronym, \ldawmsR. Note that the creators of the
proposal intentionally chose the phrase ``lawful access'' over ``\acl{EA}'' in order to emphasize the role of legal
process and dispel the negative stigma that accompanies \ac{EA}. I refer to \ldawmsr as an \ac{EA} proposal, but use the
term entirely in the spirit of their paper.

@@

\newcommand{\threattablebegin}[3]{
  \begin{FlushLeft}
    \small
    \begin{longtable}{ lp{3cm}p{5.2cm}p{6cm} }
      \caption{#1 Threats}
      \label{table-#2}
      \\ \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\ \midrule
      \endfirsthead
      \caption[]{#1 Threats (continued)}
      \\
      \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\
      % \midrule
      \endhead
      \endfoot
      \bottomrule
      \endlastfoot
}

@@

@@

% Economics: vastly increases costs and barrier to entry for vendors.

%%%%%%%%%%%%
% Old notes for reference
% -----------------------
% Chapter 4, threat models
% (how to be specific enough to be useful but generic enough to apply to many systems? Focus on the EA type (DAR v DIM),
%   then apply to specific systems)
% DAR, DIM threat models (make sure to cover abelson_2015)
% Basic proposals
%  --> mappings onto threat models
% At work: 3 example systems analyzed with this threat model
% 1. IM (E2E IM too?) -- in motion
% 2. Cloud storage -- at rest
% 3. Mobile phone -- at rest, but way different scenario than cloud
%  --> include Ozzie's CLEAR, since it was higher profile
%%%%%%%%%%%%

>>>>

This chapter consists of a threat model and analysis of a specific device key escrow \ac{EA} proposal, Stefan Savage's
``Lawful Device Access without Mass Surveillance Risk: A Technical Design Discussion'' \cite{savage_lawful_2018}.
Lacking a concise name, this proposal will be referred to by its acronym, \ldawmsR. This chapter assumes that the
proposal is accompanied by some legal framework regulating its application and use, though it is not the focus of this
analysis, and nothing is assumed about it in particular. Note that the creators of the proposal intentionally chose the
phrase ``lawful access'' over ``\acl{EA}'' in order to emphasize the role of legal process and dispel the negative
stigma that accompanies \ac{EA}. I refer to \ldawmsr as an \ac{EA} proposal, but use the term entirely in the spirit of
their paper.

@@

\newcommand{\threattablebegin}[3]{
  \begin{FlushLeft}
    \small
    \singlespacing
    \begin{longtable}{ lp{3cm}p{5.2cm}p{6cm} }
      \caption{#1 Threats}
      \label{table-#2}
      \\ \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\ \midrule
      \endfirsthead
      \caption[]{#1 Threats (continued)}
      \\
      \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\
      % \midrule
      \endhead
      \endfoot
      \bottomrule
      \endlastfoot
}

@@

This chapter began with a list of goals by which \ac{DAR} \ac{EA} proposals can be measured, including security,
protection of civil liberties, transparency, law enforcement utility, and economic impact. In this section I measure
\ldawmsr against each of these goals.

@@

\paragraph*{Security} Security is the main topic of this chapter, and has already been discussed thoroughly. \ldawmsr
introduces significant risk in the DID-DSK database itself, but does a good job in many other respects, especially if
the recommended mitigations are implemented. It goes from very hard to attack, when everything is working as intended,
to simple to attack, when the database is leaked. However, even when it becomes trivial to attack, the impact is limited
to devices in physical possession and cannot be hidden from the device user.

\paragraph*{Protection of civil liberties} This goal was defined as defending against mass surveillance and abuse by
authoritarian regimes. This proposal does an excellent job of protecting against mass surveillance due to its
physicality. Any power cannot abuse this technology at scale. It is not as strong at protecting against authoritarian
regimes. Prior to a leak, vendors would face intense and possibly coercive legal pressure to unlock devices in foreign
countries. After a leak, these regimes could get into any device they want. If one lived in a country that was willing
to take and destroy their devices to read their contents without legal due process, this would be an unwelcome
technology.

\paragraph*{Transparency} \ldawmsr excels at transparency on the device, but fails at transparency to the public. Due to
destructive disassembly (or the hardware transparency mechanism), whether a device has been accessed using this method
is irrefutable. However, this is only possible to confirm if the device is available. If it is stolen and unlocked by
criminals or is lawfully accessed under secretive conditions, both the user and the public have no way of knowing. This
leaves open the possibility for government abuse---though again with the caveat that physical possession requirements
mean it cannot be abused without a trace.

\paragraph*{Law enforcement utility} This proposal involves a few tradeoffs between security and law enforcement
utility. The physical possession, time vault, and limited number of authorized law enforcement laboratory requirements
each insert a barrier to usability. The physical possession requirement is far too important for security and civil
liberties to sacrifice for utility. Furthermore, law enforcement, and search and seizure law generally, is geared
towards physical evidence already. The time vault prevents against time-sensitive threats, though destructive
disassembly (not part of the original proposal) may be enough to cover these cases as well, so the time vault could be
decreased without significant impact. Limiting the number of parties able to use the system mitigates spoofing attacks;
local law enforcement would have to cooperate with one of these parties, such as a regional \ac{FBI} office. (This
really just shifts the spoofing threat up a level, though the shift is appropriate.) In the end, law enforcement still
has a reliable way to get into lawfully seized devices. \ldawmsr upholds its end; the onus is on the government to fund
the \ac{FBI} operation and cultivate cooperation between local and federal agencies.

\paragraph*{Economic impact} Economic costs to the vendor fall into three categories---implementing the design, running
the system, and absorbing lost business. Even once a proposal like \ldawmsr was refined enough to be implemented, the
vendor would need to update hardware designs and create the software systems to get it started. Once in use, the vendor
would face considerable costs in running it securely, considering the supreme importance of transporting and storing the
unlock artifacts safely. Finally, the vendor would certainly lose privacy-conscious customers to vendors not under the
system, whether small businesses, foreign competitors, or resellers offering pre-\ac{EA} devices. The scale of these
costs relative to device manufacturer's naturally large size is unclear. Costs to the government include the \ac{FBI}
operation and a necessary scale-up in training and resources available to state and local law enforcement. Government
reimbursement for vendor compliance costs has precedent in laws like \acs{CALEA}, and could be applied to a \ac{DAR}
\ac{EA} regulation as well \cite{edwards_hr4922_1994}.
